Combinatorial Mixture Models for Single--Cell Assays with Application to Vaccine Studies

### 2012-07-26 MIMOSA.tex
Set to one-column layout. split some equations over multiple lines so they fit on one or two column layout.
Signed-off-by: Greg Finak <gfinak@fhcrc.org>
Added simulations for N=1000 in the appendix. Added refs
Signed-off-by: Greg Finak <gfinak@fhcrc.org>

%\documentclass[11pt]{article}
\documentclass[useAMS,usenatbib]{biom}
\def\bSig\mathbf{\Sigma}
\newcommand{\VS}{V\&S}
\newcommand{\tr}{\mbox{tr}}
%\usepackage{geometry,authblk,multicol,amsmath}
\usepackage{amsmath,tikz}
\usetikzlibrary{calc}
\usetikzlibrary{positioning}

@@

\subsection{Parameter estimation}
\label{s:estimation}
Our estimation algorithms make direct use of the marginal likelihoods, $\mathrm{L}_0$ and $\mathrm{L}_1$, obtained after integrating out the $p_{\{s,u\}i}$'s for the null and alternative models, which greatly simplify our calculations. Given the conjugacy of the priors, the marginal likelihoods $\mathrm{L}_0$ and $\mathrm{L}_1$ are available in closed forms (Web Appendix XX), and are given by,
 \begin{align*}
 \begin{split}
  	&\mathrm{L}_0(\alpha_u,\beta_u|\mathbf{y})
	=\prod_{i=1}^P\binom{N_{ui}}{n_{ui}}\binom{N_{si}}{n_{si}}\cdot\\ &\frac{\mathrm{B}(n_{si}+n_{ui}+\alpha_u,N_{si}-n_{si}+N_{ui}-n_{ui}+\beta_u)}{\mathrm{B}(\alpha_u,\beta_u)}
	\end{split}
 \end{align*}

and
\begin{align}
	\begin{split}
&\mathrm{L}_1(\alpha_u,\beta_u,\alpha_s,\beta_s|\mathbf{y}) 
=\prod_{i=1}^P\binom{N_{ui}}{n_{ui}} \binom{N_{si}}{n_{si}}\cdot\\ &\frac{\mathrm{B}(n_{ui}+\alpha_u,N_{ui}-n_{ui}+\beta_u)}{\mathrm{B}(\alpha_u,\beta_u)}\frac{\mathrm{B}(n_{si}+\alpha_s,N_{si}-n_{si}+\beta_s)}{\mathrm{B}(\alpha_s,\beta_s)}
\label{model2:unconstrained}
\end{split}
\end{align}
Assuming that the missing data, the $z_i$'s, are known, we define the complete data log-likelihood as follows,
\begin{equation}
\begin{split}
l(\boldsymbol{\theta}|\mathbf{y},\mathbf{z})=\sum_i z_i l_0(\alpha_u, \beta_u|\mathbf{y}_i) +(1-z_i) l_1(\alpha_u, \beta_u, \alpha_s, \beta_s|\mathbf{y}_i)+\\z_i\log(w)+(1-z_i)\log(1-w)\label{eq:cll}
\end{split}
\end{equation}
where $l_0$ and $l_1$ are the log marginal-likelihoods and $\boldsymbol{\theta}\equiv(\alpha_u, \beta_u, \alpha_s,\beta_s, w)$ is the vector of parameters to be estimated. In the one-sided case, the alternative prior specification must satisfy the constraint $p_s>p_u$, and the marginal likelihood derivation involves the calculation of a normalizing constant that is not available in closed form but can easily be estimated. All calculations for the one-sided case are described in Web Appendix XX.

@@

\subsection{MCMC algorithm}
Realizations were generated from the posterior distribution via MCMC algorithms~\citep{Gelfand:1996wc}. All updates were done via Metropolis-Hastings sampling except for the $z_i$'s and $w$ that were done via Gibbs samplings.
Details about the algorithms are given in Web Appendix XX. We used the method of \cite{Raftery:1992vp,Raftery:1996ws} to determine the number of iterations, based on a short pilot run of the sampler. For each dataset presented here, this suggested that a sample of no more than about 1,000,000 iterations with 50,000 burn-in iterations was sufficient to estimate standard posterior quantities. Guided by this, and leaving some margin, we used 2,000,000 iterations after 50,000  burn-ins for each dataset explored here.

@@

\subsection{Parameter estimation}
Again, to simplify the estimation problem, we make use of the marginal likelihoods that can be obtained in closed forms (see Web Appendix XX). For the null component, the marginal likelihood $\mathrm{L}_0$ is given by,
\begin{align*}
\mathrm{L}_0(\boldsymbol{\alpha}_u|\mathbf{n}_s,\mathbf{n}_u) &= \prod_{i=0}^I\frac{ \mathrm{B}(\boldsymbol{\alpha}_{u}+\mathbf{n}_{ui}+\mathbf{n}_{si})}{\mathrm{B}(\boldsymbol{\alpha}_u)} \cdot \frac{N_{si}!}{\prod_k n_{sik}!} \cdot \frac{N_{ui}!}{\prod_k n_{uik}!}
\end{align*}
where $\mathrm{B}$ is the $2^K$-dimensional Beta function defined as $\mathrm{B}(\boldsymbol{\alpha})=\prod_k\Gamma(\alpha_k)/\Gamma(\sum_k\alpha_k)$. Similarly the marginal likelihood for the alternative model is given by 
\begin{align*}
\begin{split}
\mathrm{L}_1(\boldsymbol{\alpha}_u,\boldsymbol{\alpha}_s|\mathbf{n}_s,\mathbf{n}_u) =& \prod_{i=0}^I\frac{\mathrm{B}(\boldsymbol{\alpha}_{u}+\mathbf{n}_{ui}) \mathrm{B}(\boldsymbol{\alpha}_{s}+\mathbf{n}_{si})}{\mathrm{B}(\boldsymbol{\alpha}_s)\mathrm{B}(\boldsymbol{\alpha}_u)} \cdot \frac{N_{si}!}{\prod_k n_{sik}!} \cdot \\ &\frac{N_{ui}!}{\prod_k n_{uik}!}.%\label{eq:postmult}
\end{split}
\end{align*}
The estimation procedures (both EM and MCMC based) for the multinonial-Dirichlet are the same as for the beta-binomial model except that the number of parameters to be estimated is larger. In our experience, the performance of the EM algorithm greatly deteriorates when $K$ becomes larger than three. It becomes highly dependent on the initial values and can fail to converge in many instances. Although our MCMC algorithm is slightly more computational, it does not suffer from this problem and provides a robust alternative when $K$ is large. More details about both algorithms are given in Web Appendix XX.

@@

\section{Discussion}
\label{s:discussion}
Experimentalists have already access to a myriad of single-cell assays such as flow cytometry, mass cytometry and multiplexed quantitative-PCR, to name a few. Single--cell assays will become even more routine once sequencing at the single-cell level becomes practical (Ref to RNA-Seq single--cell). As a consequence, the development of effective statistical methods to detect differences in gene or protein expression at the single--cell level is becoming increasingly important. Current approaches for single-cell assays are for the most part simplistic (t-test, $\chi^2$ test, Fisher's exact test), and resulting inference can be quite unreliable especially when the cell counts are small. Most importantly, these methods do not share information across samples, resulting in less power to detect true differences than empirical-Bayes and hierarchical modeling approaches, which are widely applied in the microarray literature~\citep{Kendziorski:2003uw,Newton:2001go,Smyth:2005iy}. In addition, most of these methods are univariate in nature and inappropriate for high dimensional next generation single--cell assay.

@@

Detecting differences in poly-functional cell populations (\textit{i.e.} identifying changes in cell populations that co-express multiple proteins, cytokines, or genes), is important in immunology, since it allows the identification of more precisely defined, more homogeneous cell populations~\citep{Milush:2009bz}. In the context of HIV, these poly-functional cell populations have been shown to be correlated with good outcome such as vaccine protection and long-term disease non-progression (ADD REFERENCES TO THE PAPERS STEVE SUGGESTED IN THE GRANT). In the ICS data used here, the stimulation is expected to only increase the number of antigen specific cells detected. It  follows that if a specific cell subset expressing multiple markers is being differentially expressed, differential expression based on the marginal cell counts should also be detected. As such, identifying poly-functional cytokine profiles from ICS data can be done in an iterative way. First univariate tests on marginal populations are performed and then specific cell subsets expressing the positive markers detected are then tested. Even in this situation, this iterative (univariate) approach might not be satisfactory due to the large number of possible combinations that needs to be tested, and a multivariate approach might be preferable. In this case, as others have pointed out, in order to have the most power to detect a true difference, the statistical test should be selected taking into account only the cytokine combinations of interest~\citep{Nason:2006dx}.

@@

Web Appendices A and B, and Web Figures A and B referenced in Sections \ref{s:data} and \ref{s:DEone} are available in the attached Web-based supplementary material.\vspace*{-8pt}
% This will be replaced at submission time
%at the Biometrics website on Wiley Online Library.

@@

@@

%\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
%   \centering
%%   \includegraphics[width=.75\columnwidth]{Figures/2}\\ 
%%   \includegraphics[width=.75\columnwidth]{Figures/12} 
%\begin{tikzpicture}
%    \node[anchor=south west, inner sep=0] at (0,0){\includegraphics[width=.5\columnwidth]{Figures/14}};
%    \node[anchor=south west, inner sep=0] at (8,0){\includegraphics[width=.5\columnwidth]{Figures/15}};
%    \node[anchor=south west, inner sep=0] at (0,-3.75){\includegraphics[width=.5\columnwidth]{Figures/16}};
%
%
%    \node at (0,3.4) [font=\tiny\sffamily] {A} ;
%    \node at (8,3.4) [font=\tiny\sffamily] {B} ;
%    \node at (0,-0.5) [font=\tiny\sffamily] {C} ;
%    \end{tikzpicture}
%   \caption{Comparison of MIMOSA on other cytokines and cytokine combinations for ENV-1-PTEG and GAG-1-PTEG stimulated CD4+ T-cells from the HVTN065 trial.}
%\label{fig:HVTN065ResultsCont}
%\end{figure}
\subsection{Web Figure B: Other Simulation Results}
\begin{figure} %  figure placement: here, top, bottom, or page
   \centering
\begin{tikzpicture} [auto,node distance=0cm]
\node at (0,0) (A) {
\begin{tikzpicture}
    \node[anchor=south west,inner sep=0] at (0,0) (a) {\includegraphics[width=0.4\columnwidth]{Figures/Sim_Twosided_ROC_5000.pdf}};
    \begin{scope} [x={(a.south east)},y={(a.north west)}]
        \node at (0,1) [font=\tiny\sffamily] {A} ;
    \end{scope}
    \end{tikzpicture}
    };
    \node [right=of A] (B) {
    \begin{tikzpicture}
    \node[anchor=south west, inner sep=0] at (0,0) (b) {\includegraphics[width=0.4\columnwidth]{Figures/Sim_Twosided_FDR_5000.pdf}};
        \begin{scope} [x={(b.south east)},y={(b.north west)}]
        \node at (0,1) [font=\tiny\sffamily] {B} ;
        \end{scope}
    \end{tikzpicture}
    };
    \node [below=of A] (C) {
    \begin{tikzpicture}
     \node[anchor=south west,inner sep=0] at (0,0) (c) {\includegraphics[width=0.4\columnwidth]{Figures/Sim_Truncated_ROC_5000.pdf}};
         \begin{scope} [x={(c.south east)},y={(c.north west)}]
                 \node at (0,1) [font=\tiny\sffamily] {C} ;
	\end{scope}
     \end{tikzpicture}
     };
     \node [below=of B] (D) {
     \begin{tikzpicture}
    \node[anchor=south west, inner sep=0] at (0,0) (d) {\includegraphics[width=0.4\columnwidth]{Figures/Sim_Truncated_FDR_5000.pdf}};
        \begin{scope} [x={(d.south east)},y={(d.north west)}]
            \node at (0,1) [font=\tiny\sffamily] {D} ;
\end{scope}
    \end{tikzpicture}
    };
 \end{tikzpicture}
   \caption{Unconstrained MIMOSA model fit to two--sided data (A-B) or to data where model assumptions are violated (C-D). Two--sided data were simulated from a standard model. A) Average ROC curves from 10 simulations and B) average observed vs nominal FDR from 10 simulations at N=5,000. Unconstrained MIMOSA fit to two--sided data simulated from a model where the proportions were drawn from a truncated normal distribution over $[0,1]$, rather than a Beta distribution. C) Average ROC curves from 10 simulations and D) average observed vs nominal FDR from 10 simulations at N=5,000. }
   \label{webfig:simulations_trunc}
\end{figure}

>>>>

%\documentclass[11pt]{article}
\documentclass[useAMS,referee,usenatbib]{biom}
\def\bSig\mathbf{\Sigma}
\newcommand{\VS}{V\&S}
\newcommand{\tr}{\mbox{tr}}
%\usepackage{geometry,authblk,multicol,amsmath}
\usepackage{amsmath,tikz}
\usetikzlibrary{calc}
\usetikzlibrary{positioning}

@@

\subsection{Parameter estimation}
\label{s:estimation}
Our estimation algorithms make direct use of the marginal likelihoods, $\mathrm{L}_0$ and $\mathrm{L}_1$, obtained after integrating out the $p_{\{s,u\}i}$'s for the null and alternative models, which greatly simplify our calculations. Given the conjugacy of the priors, the marginal likelihoods $\mathrm{L}_0$ and $\mathrm{L}_1$ are available in closed forms (Web Appendix C), and are given by,
 \begin{align*}
 \begin{split}
  	&\mathrm{L}_0(\alpha_u,\beta_u|\mathbf{y})
	=\prod_{i=1}^P\binom{N_{ui}}{n_{ui}}\binom{N_{si}}{n_{si}}\cdot\\ &\frac{\mathrm{B}(n_{si}+n_{ui}+\alpha_u,N_{si}-n_{si}+N_{ui}-n_{ui}+\beta_u)}{\mathrm{B}(\alpha_u,\beta_u)}
	\end{split}
 \end{align*}

and
\begin{align}
	\begin{split}
&\mathrm{L}_1(\alpha_u,\beta_u,\alpha_s,\beta_s|\mathbf{y}) 
=\prod_{i=1}^P\binom{N_{ui}}{n_{ui}} \binom{N_{si}}{n_{si}}\cdot\\ &\frac{\mathrm{B}(n_{ui}+\alpha_u,N_{ui}-n_{ui}+\beta_u)}{\mathrm{B}(\alpha_u,\beta_u)}\frac{\mathrm{B}(n_{si}+\alpha_s,N_{si}-n_{si}+\beta_s)}{\mathrm{B}(\alpha_s,\beta_s)}
\label{model2:unconstrained}
\end{split}
\end{align}
Assuming that the missing data, the $z_i$'s, are known, we define the complete data log-likelihood as follows,
\begin{equation}
\begin{split}
l(\boldsymbol{\theta}|\mathbf{y},\mathbf{z})=\sum_i z_i l_0(\alpha_u, \beta_u|\mathbf{y}_i) +(1-z_i) l_1(\alpha_u, \beta_u, \alpha_s, \beta_s|\mathbf{y}_i)+\\z_i\log(w)+(1-z_i)\log(1-w)\label{eq:cll}
\end{split}
\end{equation}
where $l_0$ and $l_1$ are the log marginal-likelihoods and $\boldsymbol{\theta}\equiv(\alpha_u, \beta_u, \alpha_s,\beta_s, w)$ is the vector of parameters to be estimated. In the one-sided case, the alternative prior specification must satisfy the constraint $p_s>p_u$, and the marginal likelihood derivation involves the calculation of a normalizing constant that is not available in closed form but can easily be estimated. All calculations for the one-sided case are described in Web Appendix B.

@@

\subsection{MCMC algorithm}
Realizations were generated from the posterior distribution via MCMC algorithms~\citep{Gelfand:1996wc}. All updates were done via Metropolis-Hastings sampling except for the $z_i$'s and $w$ that were done via Gibbs samplings.
Details about the algorithms are given in Web Appendix D. We used the method of \cite{Raftery:1992vp,Raftery:1996ws} to determine the number of iterations, based on a short pilot run of the sampler. For each dataset presented here, this suggested that a sample of no more than about 1,000,000 iterations with 50,000 burn-in iterations was sufficient to estimate standard posterior quantities. Guided by this, and leaving some margin, we used 2,000,000 iterations after 50,000  burn-ins for each dataset explored here.

@@

\subsection{Parameter estimation}
Again, to simplify the estimation problem, we make use of the marginal likelihoods that can be obtained in closed forms (see Web Appendix E). For the null component, the marginal likelihood $\mathrm{L}_0$ is given by,
\begin{align*}
\mathrm{L}_0(\boldsymbol{\alpha}_u|\mathbf{n}_s,\mathbf{n}_u) &= \prod_{i=0}^I\frac{ \mathrm{B}(\boldsymbol{\alpha}_{u}+\mathbf{n}_{ui}+\mathbf{n}_{si})}{\mathrm{B}(\boldsymbol{\alpha}_u)} \cdot \frac{N_{si}!}{\prod_k n_{sik}!} \cdot \frac{N_{ui}!}{\prod_k n_{uik}!}
\end{align*}
where $\mathrm{B}$ is the $2^K$-dimensional Beta function defined as $\mathrm{B}(\boldsymbol{\alpha})=\prod_k\Gamma(\alpha_k)/\Gamma(\sum_k\alpha_k)$. Similarly the marginal likelihood for the alternative model is given by 
\begin{align*}
\begin{split}
\mathrm{L}_1(\boldsymbol{\alpha}_u,\boldsymbol{\alpha}_s|\mathbf{n}_s,\mathbf{n}_u) =& \prod_{i=0}^I\frac{\mathrm{B}(\boldsymbol{\alpha}_{u}+\mathbf{n}_{ui}) \mathrm{B}(\boldsymbol{\alpha}_{s}+\mathbf{n}_{si})}{\mathrm{B}(\boldsymbol{\alpha}_s)\mathrm{B}(\boldsymbol{\alpha}_u)} \cdot \frac{N_{si}!}{\prod_k n_{sik}!} \cdot \\ &\frac{N_{ui}!}{\prod_k n_{uik}!}.%\label{eq:postmult}
\end{split}
\end{align*}
The estimation procedures (both EM and MCMC based) for the multinonial-Dirichlet are the same as for the beta-binomial model except that the number of parameters to be estimated is larger. In our experience, the performance of the EM algorithm greatly deteriorates when $K$ becomes larger than three. It becomes highly dependent on the initial values and can fail to converge in many instances. Although our MCMC algorithm is slightly more computational, it does not suffer from this problem and provides a robust alternative when $K$ is large. More details about both algorithms are given in Web Appendix D.

@@

\section{Discussion}
\label{s:discussion}
Experimentalists have already access to a myriad of single-cell assays such as flow cytometry, mass cytometry and multiplexed quantitative-PCR, to name a few. Single--cell assays will become even more routine once sequencing at the single-cell level becomes practical~\citep{Ramskold:2012gj}. As a consequence, the development of effective statistical methods to detect differences in gene or protein expression at the single--cell level is becoming increasingly important. Current approaches for single-cell assays are for the most part simplistic (t-test, $\chi^2$ test, Fisher's exact test), and resulting inference can be quite unreliable especially when the cell counts are small. Most importantly, these methods do not share information across samples, resulting in less power to detect true differences than empirical-Bayes and hierarchical modeling approaches, which are widely applied in the microarray literature~\citep{Kendziorski:2003uw,Newton:2001go,Smyth:2005iy}. In addition, most of these methods are univariate in nature and inappropriate for high dimensional next generation single--cell assay.

@@

Detecting differences in poly-functional cell populations (\textit{i.e.} identifying changes in cell populations that co-express multiple proteins, cytokines, or genes), is important in immunology, since it allows the identification of more precisely defined, more homogeneous cell populations~\citep{Milush:2009bz}. In the context of HIV, these poly-functional cell populations have been shown to be correlated with good outcome such as vaccine protection and long-term disease non-progression~\citep{Betts:2006dw,Darrah:2007ih,Precopio:2007ht}. In the ICS data used here, the stimulation is expected to only increase the number of antigen specific cells detected. It  follows that if a specific cell subset expressing multiple markers is being differentially expressed, differential expression based on the marginal cell counts should also be detected. As such, identifying poly-functional cytokine profiles from ICS data can be done in an iterative way. First univariate tests on marginal populations are performed and then specific cell subsets expressing the positive markers detected are then tested. Even in this situation, this iterative (univariate) approach might not be satisfactory due to the large number of possible combinations that needs to be tested, and a multivariate approach might be preferable. In this case, as others have pointed out, in order to have the most power to detect a true difference, the statistical test should be selected taking into account only the cytokine combinations of interest~\citep{Nason:2006dx}.

@@

Web Appendices A, B, C, D, and E, and Web Figures A and B referenced in Sections \ref{s:data} and \ref{s:DEone},\ref{s:estimation},  and \ref{s:demarkercombos} are available in the attached Web-based supplementary material.\vspace*{-8pt}
% This will be replaced at submission time
%at the Biometrics website on Wiley Online Library.

@@

\subsection{Web Appendix C: Derivation of Marginal Likelihoods for Beta--Binomial Model}

\subsection{Web Appendix D: The MCMC Algorithm}

\subsection{Web Appendix E: Marginal Likelihoods for the Multivariate Model}

@@

%\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
%   \centering
%%   \includegraphics[width=.75\columnwidth]{Figures/2}\\ 
%%   \includegraphics[width=.75\columnwidth]{Figures/12} 
%\begin{tikzpicture}
%    \node[anchor=south west, inner sep=0] at (0,0){\includegraphics[width=.5\columnwidth]{Figures/14}};
%    \node[anchor=south west, inner sep=0] at (8,0){\includegraphics[width=.5\columnwidth]{Figures/15}};
%    \node[anchor=south west, inner sep=0] at (0,-3.75){\includegraphics[width=.5\columnwidth]{Figures/16}};
%    \node at (0,3.4) [font=\tiny\sffamily] {A} ;
%    \node at (8,3.4) [font=\tiny\sffamily] {B} ;
%    \node at (0,-0.5) [font=\tiny\sffamily] {C} ;
%    \end{tikzpicture}
%   \caption{Comparison of MIMOSA on other cytokines and cytokine combinations for ENV-1-PTEG and GAG-1-PTEG stimulated CD4+ T-cells from the HVTN065 trial.}
%\label{fig:HVTN065ResultsCont}
%\end{figure}
\subsection{Web Figure B: Additional Simulation Results}
\begin{figure} %  figure placement: here, top, bottom, or page
   \centering
\begin{tikzpicture} [auto,node distance=0cm]
\node at (0,0) (A) {
\begin{tikzpicture}
    \node[anchor=south west,inner sep=0] at (0,0) (a) {\includegraphics[width=0.4\columnwidth]{Figures/Sim_Twosided_ROC_5000.pdf}};
    \begin{scope} [x={(a.south east)},y={(a.north west)}]
        \node at (0,1) [font=\tiny\sffamily] {A} ;
    \end{scope}
    \end{tikzpicture}
    };
    \node [right=of A] (B) {
    \begin{tikzpicture}
    \node[anchor=south west, inner sep=0] at (0,0) (b) {\includegraphics[width=0.4\columnwidth]{Figures/Sim_Twosided_FDR_5000.pdf}};
        \begin{scope} [x={(b.south east)},y={(b.north west)}]
        \node at (0,1) [font=\tiny\sffamily] {B} ;
        \end{scope}
    \end{tikzpicture}
    };
    \node [below=of A] (C) {
    \begin{tikzpicture}
     \node[anchor=south west,inner sep=0] at (0,0) (c) {\includegraphics[width=0.4\columnwidth]{Figures/Sim_Truncated_ROC_5000.pdf}};
         \begin{scope} [x={(c.south east)},y={(c.north west)}]
                 \node at (0,1) [font=\tiny\sffamily] {C} ;
	\end{scope}
     \end{tikzpicture}
     };
     \node [below=of B] (D) {
     \begin{tikzpicture}
    \node[anchor=south west, inner sep=0] at (0,0) (d) {\includegraphics[width=0.4\columnwidth]{Figures/Sim_Truncated_FDR_5000.pdf}};
        \begin{scope} [x={(d.south east)},y={(d.north west)}]
            \node at (0,1) [font=\tiny\sffamily] {D} ;
\end{scope}
    \end{tikzpicture}
    };
  \node [below=of C] (E) {
\begin{tikzpicture}
    \node[anchor=south west,inner sep=0] at (0,0) (e) {\includegraphics[width=0.4\columnwidth]{Figures/Sim_Twosided_ROC_1000.pdf}};
    \begin{scope} [x={(e.south east)},y={(e.north west)}]
        \node at (0,1) [font=\tiny\sffamily] {E} ;
    \end{scope}
    \end{tikzpicture}
    };
    \node [right=of E] (F) {
    \begin{tikzpicture}
    \node[anchor=south west, inner sep=0] at (0,0) (f) {\includegraphics[width=0.4\columnwidth]{Figures/Sim_Twosided_FDR_1000.pdf}};
        \begin{scope} [x={(f.south east)},y={(f.north west)}]
        \node at (0,1) [font=\tiny\sffamily] {F} ;
        \end{scope}
    \end{tikzpicture}
    };
    \node [below=of E] (G) {
    \begin{tikzpicture}
     \node[anchor=south west,inner sep=0] at (0,0) (g) {\includegraphics[width=0.4\columnwidth]{Figures/Sim_Truncated_ROC_1000.pdf}};
         \begin{scope} [x={(g.south east)},y={(g.north west)}]
                 \node at (0,1) [font=\tiny\sffamily] {G} ;
	\end{scope}
     \end{tikzpicture}
     };
     \node [below=of F] (H) {
     \begin{tikzpicture}
    \node[anchor=south west, inner sep=0] at (0,0) (h) {\includegraphics[width=0.4\columnwidth]{Figures/Sim_Truncated_FDR_1000.pdf}};
        \begin{scope} [x={(h.south east)},y={(h.north west)}]
            \node at (0,1) [font=\tiny\sffamily] {H} ;
\end{scope}
    \end{tikzpicture}
    };
 \end{tikzpicture}
   \caption{Unconstrained MIMOSA model fit to two--sided data (A,B,E,F) or to data where model assumptions are violated (C,D,G,H). Two--sided data were simulated from a standard model. A) Average ROC curves and B) average observed vs nominal FDR from 10 simulations with N=5,000, and E-F) N=1,000. Unconstrained MIMOSA fit to two--sided data simulated from a model where the proportions were drawn from a truncated normal distribution over $[0,1]$, rather than a Beta distribution. C) Average ROC curves and D) average observed vs nominal FDR from 10 simulations at N=5,000, and G-H) N=1,000. }
   \label{webfig:simulations_trunc}
\end{figure}
